A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-09 docs/methods/erosion_methods.tex
Revisions

To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times. The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation. As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back---somewhat reminiscent of an American football.  Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces. The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively. At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body. However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves). The absolute stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red). Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time.

>>>>

To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times. The interfaces are color-coded by normalized time $t/t_f$, where $t_f = 1.79 \times 10^{-2}$ is the time at which the body vanishes in the simulation. As seen in Fig.~\ref{shrink_intface}(a), the body converges to a fairly slender, for-aft symmetric shape that has corners at its front and back---somewhat reminiscent of an American football.  Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces. The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = $ 0 and 0.5 corresponding to the rear and front stagnation points respectively. At early times (yellow curves), the stress varies significantly, with more stress concentrated at the top and bottom of the body. However, as erosion reshapes the body, the stress becomes more uniformly distributed over the entire surface (red curves). The absolute stress $\atau$ shows slight peaks near the stagnation points as the body nears the final stages of erosion (dark red). Closer inspection reveals that the stress actually vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow with time. We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing). Interestingly, stagnation points do indeed recede in laboratory experiments on erosion  \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013}, leading us to believe that the numerical smoothing represents a real physical mechanism (see \cite{moo-ris-chi-zha-she2013} for discussion).

### 2018-07-09 docs/methods/revisions.tex
Addressing Ref 3 comments
Revisions

\noindent
\comment{The aft and rear stagnation points both recede eventhough they
are subject to zero shear. Is it just a consequence of the
regularization?}
\begin{itemize}
  \item 
\end{itemize}

>>>>

\noindent
\comment{The aft and rear stagnation points both recede even though they
are subject to zero shear. Is it just a consequence of the
regularization?}
\begin{itemize}
\item
This is a good question. Indeed, the recession of the stagnation points is a result of the numerical smoothing (both the curvature penalization and the smoothing of the stress distribution). However, in laboratory experiments, stagnation points do indeed recede, which leads us to believe that the numerical smoothing represents a real mechanism. For example, the smoothing could plausibly represent small-scale drifting of the stagnation point resulting from noise, or perhaps a second-order pressure dependence in the erosion rate. If you are interested, there is a discussion of these possibilities in Moore et al.~{\it POF} 2013.

We have added the following text at the end of section 5.1:
\begin{quotation}
We note that the recession of the stagnation points, since the stress vanishes there, is due entirely to the numerical smoothing (both the curvature penalization and the stress-distribution smoothing). Interestingly, stagnation points do indeed recede in laboratory experiments on erosion, leading us to believe that the numerical smoothing represents a real physical mechanism (see [46] for discussion).
\end{quotation}

\end{itemize}
